---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ibb

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ibb)](https://CRAN.R-project.org/package=ibb)
[![R build status](https://github.com/berkorbay/ibb/workflows/R-CMD-check/badge.svg)](https://github.com/berkorbay/ibb/actions)
<!-- badges: end -->

The goal of ibb is to access [Istanbul Metropolitan Municipality's Open Data Portal](https://data.ibb.gov.tr/en/).

## Installation

You can install the released version of ibb from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ibb")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("berkorbay/ibb")
```


## Usage and Examples

### All Data Sources

```{r}
library(ibb)

# This returns a list of data source names

(df <- get_all_data_sources())

# This returns detailed information about all data sources.
# You can use resource_id and package_id from this data in other calls.

(df <- get_all_detailed_info(verbose = FALSE))
```

### Information About a Specific Data Source

```{r}
(df <- get_detailed_info_on_data_source(package_id = "594ca91d-0c71-41da-b50a-c7cd30fab67a",
                                       get_all_info = FALSE))
```


### Get Data 
```{r}
(df <- get_data_frame_ibb(resource_id = "99d1edb6-a889-4e69-be7b-21a3f90101f1"))
```

### Pre-defined Functions for Data

There are some pre-defined functions for data download. For a full list please see the package help files.

```{r}
(df <- get_ibb_wifi_daily_data_usage())
```

## Code of Conduct

Please note that the ibb project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
